---
title: "Eyeball Boundary Timeline"
output:
  html_document:
    df_print: paged
---

Install and/or Load libraries
```{r, message=F}
if(!require(tidyverse)) install.packages("tidyverse") else require(tidyverse)
```

Create data table with video names, length of video, and range that the coarse boundaries occur.
```{r, message=F}
source("C://Users//Pro//Documents//MEGA//eyeball analysis F2017//eyeball analysis 2017//libLoad.R")
boundaryMap <- "VIDEO_NAME	videoStart	region.start	region.end	videoEnd
BasketballF1	0	164	209	376
BasketballF2	0	166	211	261
BasketballM1	0	52	97	162
BasketballM2	0	186	231	237
TennisF1    	0	218	263	262
TennisF2    	0	272	317	317
TennisM1	    0	220	265	331
TennisM2	    0	170	215	236
WeightF1    	0	225	270	372
WeightF2    	0	84	129	203
WeightM1    	0	147	192	268
WeightM2    	0	187	232	255" %>% fread
```

Print data table to check if it loaded correctly.
```{r, message=F}
boundaryMap %>% print
```

Reshape the data table from wide to long using data table. There's probably a way to do this without writing the same script twice...?
```{r, message=F}
boundaryMaplong <- melt(boundaryMap, id.vars= c("VIDEO_NAME", "region.start", "region.end"),
                        measure.vars = c("videoStart", "videoEnd"))
boundaryMaplong %>% setnames(c("variable", "value"), c("startEnd", "videoFrame"))

boundaryMaplong <- melt(data = boundaryMaplong, id.vars = c("VIDEO_NAME", "startEnd", "videoFrame"),
                        measures.vars = c("region.start", "region.end"))
boundaryMaplong %>% setnames(c("variable", "value"), c("boundaryStartEnd", "boundaryFrame"))
```

Print data table to check if it loaded correctly.
```{r, message=F}
boundaryMaplong %>% print
```

Sort by boundary time of boundary region
```{r, message=F}
ggplot() +
  geom_line(data = boundaryMaplong,
            aes(videoFrame, reorder(VIDEO_NAME, -boundaryFrame))) +
  geom_point(data = boundaryMaplong,
             aes(videoFrame, reorder(VIDEO_NAME, -boundaryFrame)),
             size = 3, shape="square") +
  
  geom_line(data = boundaryMaplong,
            aes(boundaryFrame, VIDEO_NAME, colour = VIDEO_NAME), size = 2) +
  geom_point(data = boundaryMaplong,
             aes(boundaryFrame, VIDEO_NAME, colour = VIDEO_NAME), size = 3) +
  theme(legend.position="none",
        axis.title.y = element_blank(),
        axis.text.x = element_text(angle = 45, hjust=1)) +
  labs(x="Video Frame",
       title = "Length of video and time of boundary for each Video") +
  scale_x_continuous(limits = c(0, 400),
                     breaks = seq(from=0, to=400, by = 15))
```

Sort by video length
```{r, message=F}
ggplot() +
  geom_line(data = boundaryMaplong,
            aes(videoFrame, reorder(VIDEO_NAME, -videoFrame))) +
  geom_point(data = boundaryMaplong,
             aes(videoFrame, reorder(VIDEO_NAME, -videoFrame)),
             size = 3, shape="square") +
  
  geom_line(data = boundaryMaplong,
            aes(boundaryFrame, VIDEO_NAME, colour = VIDEO_NAME), size = 2) +
  geom_point(data = boundaryMaplong,
             aes(boundaryFrame, VIDEO_NAME, colour = VIDEO_NAME), size = 3) +
  theme(legend.position="none",
        axis.title.y = element_blank(),
        axis.text.x = element_text(angle = 45, hjust=1)) +
  labs(x="Video Frame",
       title = "Length of video and time of boundary for each Video") +
  scale_x_continuous(limits = c(0, 400),
                     breaks = seq(from=0, to=400, by = 15))
```